V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298~Tau~e

### 2022-01-03 src/ms.tex
overflow issue?
accepted version

\texttt{exoplanet.TTVOrbit} worked well when fitting \planetknown, due to there being multiple transits. For \planete, we found the GP model with TTVs optimized around hyperparameters that accommodated transits where there were none; as such, we used a model without accounting for TTVs to fit the parameters for \planete. All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}. We assumed a quadratic limb darkening law, following the reparameterization described by \cite{kipping13}; this method allows for an efficient and uniform sampling of limb-darkened transit models.

>>>>

\texttt{exoplanet.TTVOrbit} worked well when fitting \planetknown, due to there being multiple transits. However, with \planete being a single-transit event, we found the GP model with TTVs optimized our hyperparameters to accommodate for transits where there were none; as such, we used a model without accounting for TTVs to fit the parameters for \planete. All other transit parameters (presented in Table~\ref{tab:table}) were initialized using values from \cite{David2019a}. We assumed a quadratic limb darkening law, following the reparameterization described by \cite{kipping13}; this method allows for an efficient and uniform sampling of limb-darkened transit models.
